Coherent optical association of a single molecule

### 2020-10-03 paper.tex
White space, regenerate PDF
Update on Overleaf.
Remove done todo
Mention ASE filter

\begin{figure*}
  \includegraphics[height=5cm]{fig1.pdf}
  \caption{Optical creation of single molecule from single atoms in tweezer.
    (A) (should label $v'=0$ and $v'=63$) Schematics of the optical transition from an atom pair to a weakly bound molecule.
    The initial state is the relative motional ground state between the two atoms
    and the final state is the first molecular bound state.
    The transition is driven by a pair of laser frequencies matching the binding energy
    of the molecule.
    The lasers are detuned from an excited molecular state in the $c^3\Sigma$ potential
    by $\Delta$ in order to suppress the scattering during the transfer.
    (B) Comparison between using a weakly bound and a deeply bound excited state
    as intermediate state for the Raman transition.
    The deeply bound excited state (upper half $v=0$) has a smaller Raman Rabi frequency ($\Omega_{Raman}$)
    compared to the weakly bound excited state (lower half $v=63$) at a given detuning.
    However, the scattering rate ($\Gamma_{scatter}$) is also much lower,
    which results in a larger Raman Rabi frequency to scattering rate ratio.
    (C) Enhancement of short range wavefunction.
    The large scattering length for the $Na(2,2),Cs(3,3)$ state creates an interaction shift
    comparable to the axial trapping frequency.
    This causes a significant change in the relative wavefunction especially at short
    intranuclear distance ($R$).
    Compared to other spin states with weaker interaction,
    the wavefunction at short distance ($R<100\mathrm{\AA}$) is significantly enhanced.
    \label{f-theory}
  }
\end{figure*}

@@

 %For a weakly bound molecular state, the spacing between states is generally smaller compared to deeply bound states and thus limits the maximum usable detuning and therefore the effectiveness of the scattering reduction by increasing the detuning. 
%Furthermore, due to similarity in wavefunction size, the weakly bound molecular ground state and initial atomic state have strong coupling with the atomic excited state which contributes significantly to the total scattering rate. The rate of such a scattering process is proportional to $1/\delta_{thresh}^2$, where $\delta_{thresh}$ is the detuning from the dissociation threshold, and thus can also be made smaller by detuning away from the dissociation threshold.
%(Should we also mention scattering of the atomic initial state too? This should affect the Raman process as well)

To find the optimal excited intermediate state, we perform a  calculation of the Raman Rabi frequency and scattering rate at different detunings from the atomic threshold taking into account of all states of the $c^3\Sigma$ excited molecular state potential (full result in SM)~\cite{Liu2017} \textcolor{red}{KW: I have only done the calculations with c3Sigma only, cause the b3Pi is highly spin orbit coupled, and not necessarily trustworthy where we are. I can also include a citation to the paper with that potential?}. As shown in Fig.~\ref{f-theory}B, the ratio of the Raman Rabi rate to scattering rate can be made larger for more deeply bound states compared to weakly bound states at a cost of a smaller Raman Rabi frequency.  %Since for a typical molecular potential the spacing between states
% decreases with increasing vibrational levels,
% a weakly bound excited molecular state
% This further increases the scattering rate for a weakly bond excited state.
% Based on these considerations, % a weakly bound excited molecular state may not be the best choice for the intermediate state in the Raman transfer. Thus,
% we calculated both the Raman Rabi frequency and the scattering rate at different detunings (full result is shown in SM). As seen in Fig.~\ref{f-theory}B,
% we found a distinct optimal regime from what has been explored experimentally previously.
%Namely, despite a smaller Raman Rabi frequency at deeply bound intermediate states, the Rabi frequency to scattering rate ratio is much higher as compared to a weakly bound intermediate state. 
As a result, we choose a deeply bound molecular excited state ($v'=0$ of $c^3\Sigma^+$) as an intermediate state to drive the Raman transition. %(mention the trend, also v=12 will work as similarly as v=0)

@@

%(mention scattering/lightshift depends on up/down matrix element ratio?)

@@

%% Transfer scheme
After the atoms are prepared in the 3322 hyperfine combination, we then perform the Raman transfer. The pulse sequence for this step is shown in Fig.~\ref{f-raman}B. Instead of adding another beam to drive the Raman transition on the atoms in the tweezer, we use the tweezer itself to achieve this goal. In particular, we turn on two co-propagating frequencies in the tweezer during the Raman pulse. The dual use of the tweezer beam ensures that there is not any undesired laser frequency that can interfere with the Raman transition, and also allows us to maximize the Raman Rabi frequency and minimize the transfer time (also minimize source of scattering). After the total tweezer power is set to the desired value, we smoothly ramp down the power of one frequency in the tweezer while simultaneously ramping up the power of a different frequency so that the total tweezer power remains unchanged. Both frequencies are kept on for a variable length of time before the process is reversed and we return to having a single frequency in the tweezer.
%\todo{clarify coprop of Raman beam?}

@@

>>>>

\begin{figure*}
  \includegraphics[height=5cm]{fig1.pdf}
  \caption{Optical creation of single molecule from single atoms in tweezer.
    (A) Schematics of the optical transition from an atom pair to a weakly bound molecule.
    The initial state is the relative motional ground state between the two atoms
    and the final state is the first molecular bound state.
    The transition is driven by a pair of laser frequencies matching the binding energy
    of the molecule.
    The lasers are detuned from an excited molecular state in the $c^3\Sigma$ potential
    by $\Delta$ in order to suppress the scattering during the transfer.
    (B) Comparison between using a weakly bound and a deeply bound excited state
    as intermediate state for the Raman transition.
    The deeply bound excited state (upper half $v=0$) has a smaller Raman Rabi frequency ($\Omega_{Raman}$)
    compared to the weakly bound excited state (lower half $v=63$) at a given detuning.
    However, the scattering rate ($\Gamma_{scatter}$) is also much lower,
    which results in a larger Raman Rabi frequency to scattering rate ratio.
    (C) Enhancement of short range wavefunction.
    The large scattering length for the $Na(2,2),Cs(3,3)$ state creates an interaction shift
    comparable to the axial trapping frequency.
    This causes a significant change in the relative wavefunction especially at short
    intranuclear distance ($R$).
    Compared to other spin states with weaker interaction,
    the wavefunction at short distance ($R<100\mathrm{\AA}$) is significantly enhanced.
    \label{f-theory}
  }
\end{figure*}

@@

% For a weakly bound molecular state, the spacing between states is generally smaller compared to deeply bound states and thus limits the maximum usable detuning and therefore the effectiveness of the scattering reduction by increasing the detuning.
%Furthermore, due to similarity in wavefunction size, the weakly bound molecular ground state and initial atomic state have strong coupling with the atomic excited state which contributes significantly to the total scattering rate. The rate of such a scattering process is proportional to $1/\delta_{thresh}^2$, where $\delta_{thresh}$ is the detuning from the dissociation threshold, and thus can also be made smaller by detuning away from the dissociation threshold.
% (Should we also mention scattering of the atomic initial state too? This should affect the Raman process as well)

To find the optimal excited intermediate state, we perform a  calculation of the Raman Rabi frequency and scattering rate at different detunings from the atomic threshold taking into account of all states of the $c^3\Sigma$ excited molecular state potential (full result in SM)~\cite{Liu2017} \textcolor{red}{KW: I have only done the calculations with c3Sigma only, cause the b3Pi is highly spin orbit coupled, and not necessarily trustworthy where we are. I can also include a citation to the paper with that potential?}. As shown in Fig.~\ref{f-theory}B, the ratio of the Raman Rabi rate to scattering rate can be made larger for more deeply bound states compared to weakly bound states at a cost of a smaller Raman Rabi frequency.  %Since for a typical molecular potential the spacing between states
% decreases with increasing vibrational levels,
% a weakly bound excited molecular state
% This further increases the scattering rate for a weakly bond excited state.
% Based on these considerations, % a weakly bound excited molecular state may not be the best choice for the intermediate state in the Raman transfer. Thus,
% we calculated both the Raman Rabi frequency and the scattering rate at different detunings (full result is shown in SM). As seen in Fig.~\ref{f-theory}B,
% we found a distinct optimal regime from what has been explored experimentally previously.
% Namely, despite a smaller Raman Rabi frequency at deeply bound intermediate states, the Rabi frequency to scattering rate ratio is much higher as compared to a weakly bound intermediate state.
As a result, we choose a deeply bound molecular excited state ($v'=0$ of $c^3\Sigma^+$) as an intermediate state to drive the Raman transition. %(mention the trend, also v=12 will work as similarly as v=0)

@@

% (mention scattering/lightshift depends on up/down matrix element ratio?)

@@

%% Transfer scheme
After the atoms are prepared in the 3322 hyperfine combination, we then perform the Raman transfer. The pulse sequence for this step is shown in Fig.~\ref{f-raman}B. Instead of adding another beam to drive the Raman transition on the atoms in the tweezer, we use the tweezer itself to achieve this goal. In particular, we turn on two co-propagating frequencies in the tweezer during the Raman pulse. The dual use of the tweezer beam ensures that there is not any undesired laser frequency that can interfere with the Raman transition, and also allows us to maximize the Raman Rabi frequency and minimize the transfer time. After the total tweezer power is set to the desired value, we smoothly ramp down the power of one frequency in the tweezer while simultaneously ramping up the power of a different frequency so that the total tweezer power remains unchanged. Both frequencies are kept on for a variable length of time before the process is reversed and we return to having a single frequency in the tweezer.
In additional to reducing the number of laser beams during the Raman transition,
we also found the spectral purity of the laser to be critical for achieving a higher
transfer efficiency. The tweezer and Raman beams are generated by amplifying a $1037 \mathrm{nm}$
external cavity diode laser (ECDL) with a Raman fiber amplifier,
which produces a broad band amplified spontaneous emission (ASE),
in addtional to the desired frequency, and increases the scattering rate due to coupline to
other excited states.
We use a bragg grating with a line width (FWHM) of $50 \mathrm{GHz}$ to clean up the
laser spectrum and found it reduces the scattering rate by at least a factor of $2$
for certain tweezer detuning.

@@

% ASE in caption for figure 4 and when mentioning the setup ahead of time
% figure 4

% ? SM?
